---
title: "JBarryStraume_Unit8CaseStudy"
author: "Jostein Barry-Straume"
date: "6/24/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Financial Applications of Time Series
## MSDS 7333 - Section 404
## Unit 4: Case Study

[Data Science @ Southern Methodist University](https://datascience.smu.edu/)

# Table of Contents
* [Team Members](#Team-Members)
* [Abstract](#Abstract)
* [Introduction](#Introduction)
* [Literature Review](#Literature-Review)
* [Background](#Background)
* [Methods](#Methods)
* [Results](#Results)
* [Future Work, Discussion, and Conclusion](#Conclusion)
* [References](#References)

# <a name="Team-Members"></a>Team Members
* [Jostein Barry-Straume](https://github.com/josteinstraume)

# <a name="Abstract"></a>Abstract

> In this case study, the application of blah blah blah is presented.

# <a name="Introduction"></a>Introduction

> Intro paragraph here

![Xkcd: Marketwatch[3]](../images/marketwatch.png)

> More intro stuff here

# <a name="Literature-Review"></a>Literature Review

> Literature review stuff here

$$SharpeRatio=\frac{\bar{r}_p - r_f} {{\sigma}_p}$$

| Symbol | Description |
| :------: | :-----------: |
| $$\bar{r}_p$$ | Represents the expected portfolio return |
| $$r_f$$ | Represents the risk free rate |
| $${\sigma}_p$$ | Represents the portfolio's standard deviation |

# <a name="Background"></a>Background

### Import Dataset

> Variable names and their descriptions for the dataset are displayed below:

| Company | Stock Ticker |
| :------: | :-----------: |
| Tesla, Inc. | TSLA |
| American Airlines | AA |
| International Business Machines Corp. (IBM) | IBM |
| General Electric (GE) | GE |
| Advanced Micro Devices, Inc. (AMD) | AMD |
| Cisco | CSCO |
| Amazon | AMZN |
| JPMorgan Chase & Co. | JPM |

> Transition to data importation

```{r}
print("Code goes here!")
```

### Summary Statistics

> The summary statistics for each company are found below:

```{r}
print("Summary stats code goes here!")
```

# <a name="Methods"></a>Methods

> Explain below code for methods

```{r}
print("methods section code goes here!")
```

# <a name="Results"></a>Results

> Results paragraph here

# <a name="Conclusion"></a>Future Work, Discussion, and Conclusion

> Paragraph 1

> Paragraph 2

> Paragraph 3

> Paragraph 4

# <a name="References"></a>References

1. Nolan and lang

2. Blah blah

3. Dummy reference
